SETI in the Spatial-Temporal Survey Domain

### 2019-05-13 paper/ms.tex
finish section5

We find no anonymously self-similar clusters of exoplanets in the \Kepler sample considered here. The cluster with the most similar period distribution consists of Kepler-1295, Kepler-1612, and Kepler-612. This triplet of systems have orbital periods within 5.1\% of each other (mean period of $P=3.82$ days).

%\citet{coughlin2014} find some correlations that are apparently removed in KOI catalog creation... due to contamination by RRlyr or other thing?
%See also TCE histogram in \citet{twicken2016}

>>>>

We find no anonymously self-similar clusters of exoplanets in the \Kepler sample considered here. The cluster with the most similar period distribution consists of Kepler-1295, Kepler-1612, and Kepler-612. This triplet of systems have orbital periods within 5.1\% of each other (mean period of $P=3.82$ days), only $2.4\sigma$ from the average of the period range distribution in Figure \ref{fig:knn}.
This cluster also has a mean separation of 0.09 deg, only slightly closer than the typical cluster separation of 0.11 deg.
